Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-04 paper/main.tex
restructure annotation and regressors

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[disable]{todonotes}
% \usepackage{todonotes}
\usepackage{units}
\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
\usepackage[
	colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

\todo[inline]{describe ``localize / isolate'' in other words}

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
The reviewed studies usually had three things in common that come along with
advantages but also disadvantages:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-designed paradigms to maximize detection power.
Further, they usually employed an explicit perceptual judgment task.
% conceptualized stimuli and blockl: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantages of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of a[n
explicit] perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Lastly, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approch improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

\todo[inline]{SE: make motivation of study clearer; gap in research; how it
    (might) adance(s) the field; make clearer how current study solves the
    problem; COH: I revised this part, it's clearer at least
if I read it now}

@@

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
fMRI time series of those 15 participants in the studyforrest dataset that took
part in all three experiments were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data were already corrected for motion and aligned by non-linear warping to a
participant-specific BOLD template image \citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant were dropped to due to invalid distortion correction
during scanning of the AO stimulus.

% preprocessing intro
All further analysis steps of the current study were carried out using tools of
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
operating system. Software packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

\subsubsection{Annotation of naturalistic stimuli}

\todo[inline]{Ich weiss nicht, ob es die etwas wild zwischendrin stehenden
    tables waren, die oft komplizierten Beschreibungen, die Länge des
    Abschnittes, oder alles zusammen, aber ich habe mich mit 2.8 extrem schwer
    getan. Bitte lass den Reviewer nicht mit dem selben Gefühl rausgehen. Gut
strukturiert, einfach und klar ist immer vom Vorteil}

@@

\todo[inline]{Simon suggested to put paragraphs regarding annotation here,
    followed by a subsection ``Regressors''. Additionally imo, it makes sense to
    build one subsection ``Stimulus annotations \& regressors'' to have a
    structure of ``AO (anno \& regressors); AV (anno \& regressors'' instead of
AO \& AV (annotation), AO \& AV (regressors)``.}

\todo[inline]{Ich würde mal die Frage antizipieren, wie gut passen die
Annotationen zu den VIS Stimuli. Und die müsste meiner Meinung nach doppelt
beantwortet werden. a) Durch genauere Beschreibung von VIS, b) durch genauere
Ausführungen, wie welche Annotation dazu passt}

% intro
Since we did not design the naturalistic stimuli for detection power, we
operationalized the perception of landscapes and landmarks (compared to e.g.
faces and objects) by annotating words spoken by the narrator of the
audio-description as well as cuts and depicted locations in the movie.
% stimuli not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
disco'', ``the platoon wades through a rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``Jenny as a
teenager'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

\todo[inline]{Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum GLM
unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter}

% table for descriptive nouns: categories, rules, examples counts
% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Descriptive nouns spoken by the audio-description's narrator that
        served as a basis to build the regressors
(see Table \ref{tab:ao-events}):
    categories, annotation rules, and examples (given in English).
    % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundaries & telephone, car \tabularnewline
objects & countable entities & wheels, plants \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & noun cueing an unfamiliar setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% table of descriptive nouns counts
\begin{table*}[h!]
    \caption{Descriptive nouns spoken by the audio-descriptions narrator:
        counts for the whole audio-only stimulus and its eight segments used
        during fMRI scanning.}
\label{tab:descr-nouns-counts}
\begin{tabular}{llllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
body & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline
bodypart &  \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline
face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline
female & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline
females & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline
fname & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline
furniture & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline
geo & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline
geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline
head & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline
male & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline
males & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline
mname & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline
object & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline
objects & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline
persons & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline
setting\_new & \anSettingnewAll & \anSettingnewI & \anSettingnewII & \anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI & \anSettingnewVII & \anSettingnewVIII \tabularnewline
setting\_rec & \anSettingrecAll &
\anSettingrecI & \anSettingrecII & \anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI & \anSettingrecVII & \anSettingrecVIII \tabularnewline
% ++ & \anAll & \anI & \anII & \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
zwischen zwei Gesichtern sein?!?}

\subsubsection{Regressors}

% first level analysis regressors AO: events
For the analysis of the AO stimulus, we created regressors correlating with the
occurrence of descriptive nouns spoken by the narrator that were added to the
original annotation of speech \citep{haeusler2020speechanno}.
% AV events
For the AV stimulus, we created regressors correlating with movie cuts provided
by another previously published annotation \citep{haeusler2016cutanno}.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}

@@

@@

%
\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter}

\todo[inline]{Habe jetzt lange darüber gebrütet: Es gibt also kaum eine
Korrelation zwischen AO und AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da
keiner weiss, was das bedeutet)}
% reference to figure ``correlation of regressors''
We computed the Pearson coefficients of the regressors across the eight segments
of both naturalistic stimuli. Results demonstrate no to minor correlations (s.
Figure \ref{fig:reg-corr}) which suggest the models should not suffer from low
detection power due to shared variance among regressors.
%
\todo[inline]{sounds meh but don't know how do write it better; results of
    correlations are given here already; maybe the short discussion (cf. very
    beginning of discussion) of these correlation could be put here too which
    will saves space in the main text; but mixing methods/results/discussion is
not absolutely "clean"}

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients  of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table \ref{tab:av-events})
        rounded to the nearest tenth.  The correlation between the two stimuli's
        root mean square loudness and between their left-right difference in
        loudness yielded the highest correlation values (\texttt{fg\_ad\_rms}
        and \texttt{fg\_av\_ger\_rms}, r=.7635 \texttt{fg\_ad\_lrdiff} and
        \texttt{fg\_av\_ger\_lrdiff}, r=.7749).} \label{fig:reg-corr}
    \end{figure*}

\todo[inline]{MH: construction of contrasts of interests feels "messy";
    consequence of the inability to filter the stimulus material. That "messy"
    part is usually not obvious from a manuscript. Here we have a fixed, complex
    stimulus, and we have to operationalize our questions with whatever we have
at hand. This is not necessarily exact, and looking at the robustness is a
feature, not a problem; COH: did not change a lot of text tbh but should be
clearer now.}

%
 \todo[inline]{Das mit den 8 kontrasten und 5 kontrasten habe ich nicht intuitiv
 durchblickt. Was wurde da gegen was kontrastiert?}
% we have fixed stimuli
Compared to previous studies we did not design the stimulus material and
experimentally controlled conditions for the purpose of optimal localization
performance since we used fixed stimuli.
% 8 + 5 contrasts
We created eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) to operationalize ``spatial perception'' compared to
``non-spatial'' perception.\todo{big ouff\dots}
% test for robustness
Creating more than just one contrast for the two fixed stimuli also let us test
for/the robustness of our results across varying ways operationalization.
% contrasts are of different quality
We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
also assumed contrasts would differ in their isolation performance because they
differ in how well the included event categories reflect on average the
preferred stimulus type processed in the PPA.
% selection of the primary contrast
Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
and discussion of the group-level and subject-specific results. Primary
contrasts were chosen based on how well the used categories on average were
assumed to match the preferred stimulus type in balance with the amount of
available data / events.

>>>>

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{comment}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[disable]{todonotes}
% \usepackage{todonotes}
\usepackage{units}
\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
\usepackage[
	colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
The reviewed studies usually had three things in common that come along with
advantages but also disadvantages:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-designed paradigms to maximize detection power.
Further, they usually employed an explicit perceptual judgment task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantages of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of a[n
explicit] perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Lastly, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approach improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

\todo[inline]{SE: make motivation of study clearer; gap in research; how it
    (might) advance(s) the field; make clearer how current study solves the
    problem; COH: I revised this part, it's clearer at least
if I read it now}

@@

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
fMRI time series of those 15 participants in the studyforrest dataset that took
part in all three experiments were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data were already corrected for motion and aligned by non-linear warping to a
participant-specific BOLD template image \citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant were dropped to due to invalid distortion correction
during scanning of the AO stimulus.
% preprocessing intro
All further analysis steps of the current study were carried out using tools of
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
operating system. Software packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

\subsubsection{Stimulus annotation and regressors}

\todo[inline]{SE: habe mich mit 2.8 extrem schwer getan: Länge des Abschnitts,
oft komplizierten Beschreibungen}

@@

\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
Ausführungen, wie welche Annotation dazu passt}

% intro
Since we did not design the naturalistic stimuli for detection power, we
annotated the temporal structure of the fixed stimuls material to operationalize
the perception of different stimulus features and create regressors for the
following GLM analysis.

\paragraph{audio-description: annotation}

% AO annotation
For the analysis of the AO data, we extended a publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% reference to table with rules and examples
A complete overview of all 18 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
disco'', ``the platoon wades through a rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``Jenny as a
teenager'').

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Categories and rules to categorize the descriptive nouns spoken by
        the audio-description's narrator. These categories served as a basis to
        build the regressors of the GLM (cf. Table \ref{tab:ao-events}).
        Examples are given in English.
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe
\tabularnewline
face & face or parts of it & face, ear, nose, mouth
\tabularnewline
female & female person & nurse, mother, woman
\tabularnewline
females & female persons & women
\tabularnewline
fname & female name & Jenny
\tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door,
window, floor, turf
\tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet
\tabularnewline
male & male person & man, father, soldier
\tabularnewline
males & male persons & boys, opponents
\tabularnewline
mname & male name & Bubba, Kennedy
\tabularnewline
object & countable entity with firm boundaries & telephone, car
\tabularnewline
objects & countable entities & wheels, plants
\tabularnewline
persons & concrete persons of unknown sex & hippies, patients
\tabularnewline
setting\_new & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
setting\_rec & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\todo[inline]{Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
    ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum
    GLM unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter;
    COH: I dropped the table of counts per segment.  The information is
    redundant since the counts are not the count of events of the actual
regressors (cf. Table \ref{tab:av-events})}

\begin{comment}
% nouns counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

\begin{table*}[h!]
    \caption{Descriptive nouns spoken by the audio-descriptions narrator:
        counts for the whole audio-only stimulus and its eight segments used
        during fMRI scanning.}
\label{tab:descr-nouns-counts}
\begin{tabular}{llllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
body & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline
bodypart &  \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline
face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline
female & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline
females & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline
fname & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline
furniture & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline
geo & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline
geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline
head & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline
male & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline
males & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline
mname & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline
object & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline
objects & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline
persons & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline
setting\_new & \anSettingnewAll & \anSettingnewI & \anSettingnewII & \anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI & \anSettingnewVII & \anSettingnewVIII \tabularnewline
setting\_rec & \anSettingrecAll &
\anSettingrecI & \anSettingrecII & \anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI & \anSettingrecVII & \anSettingrecVIII \tabularnewline
% ++ & \anAll & \anI & \anII & \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\end{comment}

% AO regressors

@@

\paragraph{audio-description: regressors}
% first level analysis regressors AO: events
For the analysis of the AO stimulus, we created regressors correlating with the
occurrence of descriptive nouns spoken by the narrator that were added to the
original annotation of speech \citep{haeusler2020speechanno}.
% AV events
For the AV stimulus, we created regressors correlating with movie cuts provided
by another previously published annotation \citep{haeusler2016cutanno}.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}

% modeling of regressors from events
Events of both stimuli were convolved with a double gamma hemodynamic response
function (HRF).

\paragraph{movie: annotation}

\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
zwischen zwei Gesichtern sein?!?; COH: that should be clearer now as the
explanation of the regressors immediately follows the description of the
annotation}

\paragraph{movie: regressors}

% AV regressors

@@

\paragraph{regressor correlations}

% reference to figure ``correlation of regressors''
We computed the Pearson coefficients of the regressors across the eight segments
of both naturalistic stimuli. Results demonstrate no to minor correlations (s.
Figure \ref{fig:reg-corr}) which suggest the models should not suffer from low
detection power due to shared variance among regressors.
%
\todo[inline]{sounds meh but don't know how do write it better; results of
    correlations are given here already; maybe the short discussion (cf. very
    beginning of discussion) of these correlation could be put here too which
    will saves space in the main text; but mixing methods/results/discussion is
not absolutely "clean"}

@@

\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter}

\todo[inline]{Habe jetzt lange darüber gebrütet: Es gibt also kaum eine
Korrelation zwischen AO und AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da
keiner weiss, was das bedeutet)}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients  of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table \ref{tab:av-events})
        rounded to the nearest tenth.  The correlation between the two stimuli's
        root mean square loudness and between their left-right difference in
        loudness yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).}
\label{fig:reg-corr}
\end{figure*}

\subsubsection{Contrasts}

\todo[inline]{Das mit den 8 kontrasten und 5 kontrasten habe ich nicht intuitiv
durchblickt. Was wurde da gegen was kontrastiert?}
% we have fixed stimuli
Compared to previous studies we did not design the stimulus material and
experimentally controlled conditions for the purpose of optimal localization
performance since we used fixed stimuli.
% 8 + 5 contrasts
We created eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) to operationalize ``spatial perception'' compared to
``non-spatial'' perception.\todo{big ouff\dots}
% test for robustness
Creating more than just one contrast for the two fixed stimuli also let us test
for/the robustness of our results across varying ways operationalization.
% contrasts are of different quality
We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
also assumed contrasts would differ in their isolation performance because they
differ in how well the included event categories reflect on average the
preferred stimulus type processed in the PPA.
% selection of the primary contrast
Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
and discussion of the group-level and subject-specific results. Primary
contrasts were chosen based on how well the used categories on average were
assumed to match the preferred stimulus type in balance with the amount of
available data / events.
